\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-04-11 main.tex
Update notebooks

\usepackage{subcaption}
\usepackage[newfloat]{minted}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{etoolbox}
\BeforeBeginEnvironment{minted}{\begin{center}\begin{tcolorbox}[width=\linewidth]}
\AfterEndEnvironment{minted}{\end{tcolorbox}\end{center}}
% \usemintedstyle[python]{vs}
\usepackage{caption}
\usepackage{xspace}
\usepackage[toc,page]{appendix}

@@

\title{SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}

@@

\begin{abstract}
Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems. Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$. Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially nonuniform magnetic penetration depth. \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting devices, and simulate the magnetic response of inhomogeneous 2D superconductors.
\end{abstract}

@@

\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
\end{equation}
where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).

@@

Because the current density has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
except at small terminals where current can be injected, one can express $\vec{J}$ in terms
of a scalar potential $g(x, y)$, called the stream function:
\begin{equation}
    \label{eq:stream}
    \vec{J}(x, y) = -\hat{z}\times\nabla g
    = \nabla\times(g\hat{z})
    = \left(\frac{\partial g}{\partial y}, -\frac{\partial g}{\partial x}\right).
\end{equation}

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function). We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z},
    \end{split}
\end{align}
where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator. (The last line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$). From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_F Q_z(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'.  
    \end{split}
\end{align}

@@

Comparing Eq.~\ref{eq:london_stream} and Eq.~\ref{eq:field_from_kernel}, we have in the plane of the film:
\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
        = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_F Q_z(\vec{r},\pvec{r}')g(\pvec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
where now $\vec{r}$ and $\pvec{r}'$ are 2D vectors, i.e. $z-z'=0$ since the film is in the same plane as itself. From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream}
    &H_{z,\,\mathrm{applied}}(\vec{r})
    = \\ &-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function.

@@

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $h$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,h}$ circulating around the hole. The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,h}$ for all points lying inside hole $h$:
\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,h}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,h}[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2
    ] I_{\mathrm{circ},\,h} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:
\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

@@

The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of magnetic flux through $S$ and the line integral of the supercurrent density $\vec{J}$ around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
\begin{equation}
    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
    \label{eq:fluxoid}
\end{equation}

@@

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $p$ points (or vertices)
which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. On the other hand, we denote element-wise multiplication with a dot: $(\mathbf{A}\cdot\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
and $(\mathbf{A}\cdot\mathbf{v})_{ij}=(\mathbf{v}\cdot\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$. $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.

The discrete version of Eq.~\ref{eq:field_from_kernel} is
\begin{align}
\begin{split}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{(\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
    % &=\mathbf{h}_{z,\,\mathrm{applied}}
    % + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}w_jg_j,
\end{split}
\end{align}
where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top line) and the equivalent discrete sum version (bottom line).

The $p\times p$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $p\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$. Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device. $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $p\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\pvec{r}')$ cf. Eq.~\ref{eq:kernels}),
and $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving the $p\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh. Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        -\mathbf{K}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,h}\mathbf{h}_{z,\,\mathrm{eff},\,h}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,h}
            & \text{inside hole }h\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

@@

\section{Laplace operator}
\label{appendix:laplace}

>>>>

\usepackage{subcaption}
\usepackage[newfloat]{minted} 
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{etoolbox}
\BeforeBeginEnvironment{minted}{\begin{center}\begin{tcolorbox}[width=\linewidth]}
\AfterEndEnvironment{minted}{\end{tcolorbox}\end{center}}
\usepackage{caption}
\usepackage{xspace}
\usepackage[toc,page]{appendix}

@@

\title{\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}

@@

\begin{abstract}
Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems. Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$. Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially nonuniform magnetic penetration depth. \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices.
\end{abstract}

@@

\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
\end{equation}
where $\Lambda=\lambda^2/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and now $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$.

@@

Because the current density has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
except at small terminals where current can be injected, one can express $\vec{J}$ in terms
of a scalar potential $g(x, y)$, called the stream function:
\begin{equation}
    \label{eq:stream}
    \vec{J}(x, y) = -\hat{z}\times\vec{\nabla}g
    = \vec{\nabla}\times(g\hat{z})
    = \left(\frac{\partial g}{\partial y}, -\frac{\partial g}{\partial x}\right).
\end{equation}

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function). We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\vec{\nabla}\times\left(\vec{\nabla}\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\vec{\nabla}(\vec{\nabla}\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z},
    \end{split}
\end{align}
where $\nabla^2=\vec{\nabla}\cdot\vec{\nabla}$ is the Laplace operator. (The last line follows from the fact that $\vec{\nabla}\cdot\left[g(x,y)\hat{z}\right] = 0$.) From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_F Q_z(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'.  
    \end{split}
\end{align}

@@

Comparing Eq.~\ref{eq:london_stream} and Eq.~\ref{eq:field_from_kernel}, we have in the plane of the film:
\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
        = \Lambda\nabla^2g)}_{z-\text{component of the total field}}
        = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_F Q_z(\vec{r},\pvec{r}')g(\pvec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
where now $\vec{r}$ and $\pvec{r}'$ are 2D vectors, i.e. $z-z'=0$ since the film is in the same plane as itself. From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream}
    &H_{z,\,\mathrm{applied}}(\vec{r})
    = \\ &-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function.

@@

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $h$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,h}$ circulating around the hole. The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,h}$ for all points lying inside hole $h$:
\begin{align}
\begin{split}
    \label{eq:Heff}
    &H_{z,\,\mathrm{eff},\,h}(\vec{r}) = \\
    &-\int_{\mathrm{hole}\,h}[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2
    ] I_{\mathrm{circ},\,h} \,\mathrm{d}^2r'.   
\end{split}
\end{align}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:
\begin{align}
\begin{split}
    \label{eq:Heff_sub}
    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r})
    = \\&-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r'.
\end{split}
\end{align}

@@

The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of magnetic flux through $S$ and the line integral of the supercurrent density $\vec{J}$ around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
\begin{equation}
    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
    \label{eq:fluxoid}
\end{equation}

@@

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:

\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $p$ points (or vertices)
which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. We denote element-wise multiplication with a lower dot, $(\mathbf{A}.\mathbf{B})_{ij}=A_{ij}B_{ij}$, and $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.

The discrete version of Eq.~\ref{eq:field_from_kernel} is
\begin{align}
\begin{split}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{(\mathbf{Q}.\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}w_jg_j,
\end{split}
\end{align}
where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top line) and the equivalent discrete sum version (bottom line).

The $p\times p$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $p\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$. Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device. $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $p\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{j}}\left(C_i + \sum_{l\neq i}q_{il}w_{l}\right),
\end{equation}
where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\pvec{r}')$ cf. Eq.~\ref{eq:kernels}),
and $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving the $p\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\nabla}^2$
is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a scalar field $f(x,y)$ defined on the mesh vertices (see~\ref{appendix:laplace}).

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh. Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\Lambda\mathbf{\nabla}^2\right)^{-1}$, we have
\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        -\mathbf{K}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,h}\mathbf{h}_{z,\,\mathrm{eff},\,h}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,h}
            & \text{inside hole }h\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

@@

\section{Mesh Laplace and gradient operators}
\label{appendix:laplace}
